Supporting Information:\\ NMRlipids IV: Headgroup \& glycerol backbone structures, and cation binding in bilayers with PE and PG lipids

### 2020-11-04 Manuscript/manuscriptPGPE.tex
Update manuscript

>>>>

\begin{figure}[]
  \centering
  \includegraphics[width=6.0cm]{../Figs/dihedralFIGS/POPC_M_G3O3_M_M_G3C4_M_M_G3C5_M_M_G3N6_MCHARMM36.png}
  \includegraphics[width=6.0cm]{../Figs/dihedralFIGS/POPC_M_G3P2_M_M_G3O3_M_M_G3C4_M_M_G3C5_MCHARMM36.png}
  \includegraphics[width=6.0cm]{../Figs/dihedralFIGS/POPC_M_G3O1_M_M_G3P2_M_M_G3O3_M_M_G3C4_MCHARMM36.png}
  \includegraphics[width=6.0cm]{../Figs/dihedralFIGS/POPC_M_G3_M_M_G3O1_M_M_G3P2_M_M_G3O3_MCHARMM36.png}
  \includegraphics[width=6.0cm]{../Figs/dihedralFIGS/POPC_M_G2_M_M_G3_M_M_G3O1_M_M_G3P2_MCHARMM36.png}
  \includegraphics[width=6.0cm]{../Figs/dihedralFIGS/POPC_M_G1_M_M_G2_M_M_G3_M_M_G3O1_MCHARMM36.png}  
  \caption{\label{DIHSwithCA}
    Changes in CHARMM36 dihedrals with increasing amount of CaCl$_2$.
  }
\end{figure}

### 2020-11-04 Manuscript/manuscriptPGPEsuppl.tex
Update manuscript

>>>>

\begin{figure}[]
  \centering
  \includegraphics[width=6.0cm]{../Figs/dihedralFIGS/POPC_M_G3O3_M_M_G3C4_M_M_G3C5_M_M_G3N6_MSlipids.png}
  \includegraphics[width=6.0cm]{../Figs/dihedralFIGS/POPC_M_G3P2_M_M_G3O3_M_M_G3C4_M_M_G3C5_MSlipids.png}
  \includegraphics[width=6.0cm]{../Figs/dihedralFIGS/POPC_M_G3O1_M_M_G3P2_M_M_G3O3_M_M_G3C4_MSlipids.png}
  \includegraphics[width=6.0cm]{../Figs/dihedralFIGS/POPC_M_G3_M_M_G3O1_M_M_G3P2_M_M_G3O3_MSlipids.png}
  \includegraphics[width=6.0cm]{../Figs/dihedralFIGS/POPC_M_G2_M_M_G3_M_M_G3O1_M_M_G3P2_MSlipids.png}
  \includegraphics[width=6.0cm]{../Figs/dihedralFIGS/POPC_M_G1_M_M_G2_M_M_G3_M_M_G3O1_MSlipids.png}  
  \caption{\label{DIHSwithCA}
    Changes in Slipids dihedrals with increasing amount of CaCl$_2$.
  }
\end{figure}

\begin{figure}[]
  \centering
  \includegraphics[width=6.0cm]{../Figs/dihedralFIGS/POPC_M_G3O3_M_M_G3C4_M_M_G3C5_M_M_G3N6_Mlipid17ecc.png}
  \includegraphics[width=6.0cm]{../Figs/dihedralFIGS/POPC_M_G3P2_M_M_G3O3_M_M_G3C4_M_M_G3C5_Mlipid17ecc.png}
  \includegraphics[width=6.0cm]{../Figs/dihedralFIGS/POPC_M_G3O1_M_M_G3P2_M_M_G3O3_M_M_G3C4_Mlipid17ecc.png}
  \includegraphics[width=6.0cm]{../Figs/dihedralFIGS/POPC_M_G3_M_M_G3O1_M_M_G3P2_M_M_G3O3_Mlipid17ecc.png}
  \includegraphics[width=6.0cm]{../Figs/dihedralFIGS/POPC_M_G2_M_M_G3_M_M_G3O1_M_M_G3P2_Mlipid17ecc.png}
  \includegraphics[width=6.0cm]{../Figs/dihedralFIGS/POPC_M_G1_M_M_G2_M_M_G3_M_M_G3O1_Mlipid17ecc.png}  
  \caption{\label{DIHSwithCA}
    Changes in lipid17ecc dihedrals with increasing amount of CaCl$_2$.
  }
\end{figure}

\begin{figure}[]
  \centering
  \includegraphics[width=6.0cm]{../Figs/dihedralFIGS/POPCsurf_M_G3O3_M_M_G3C4_M_M_G3C5_M_M_G3N6_MCHARMM36.png}
  \includegraphics[width=6.0cm]{../Figs/dihedralFIGS/POPCsurf_M_G3P2_M_M_G3O3_M_M_G3C4_M_M_G3C5_MCHARMM36.png}
  \includegraphics[width=6.0cm]{../Figs/dihedralFIGS/POPCsurf_M_G3O1_M_M_G3P2_M_M_G3O3_M_M_G3C4_MCHARMM36.png}
  \includegraphics[width=6.0cm]{../Figs/dihedralFIGS/POPCsurf_M_G3_M_M_G3O1_M_M_G3P2_M_M_G3O3_MCHARMM36.png}
  \includegraphics[width=6.0cm]{../Figs/dihedralFIGS/POPCsurf_M_G2_M_M_G3_M_M_G3O1_M_M_G3P2_MCHARMM36.png}
  \includegraphics[width=6.0cm]{../Figs/dihedralFIGS/POPCsurf_M_G1_M_M_G2_M_M_G3_M_M_G3O1_MCHARMM36.png}  
  \caption{\label{DIHSwithCA}
    Changes in CHARMM36 dihedrals with increasing amount of cationic surfactant.
  }
\end{figure}
